Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-10-06 manuscript.Rmd

exp.047 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.047[i] <- exp.047[i-1] + exp.047[i-1]*.047
}

exp.0307 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.0307[i] <- exp.0307[i-1] + exp.0307[i-1]*.0307
}

@@

years <- c(1989, 2005, 2013, 2013)
points <- c(29, n.journals.year$Journal.count[c(17,25)], max(n.journals.year$exp.05))
annotate.df <- data.frame(years, points)

@@

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.07% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))

>>>>

exp.047 <- c(31, rep(NA, 24)) 
for(i in 2:25){
    exp.047[i] <- exp.047[i-1] + exp.047[i-1]*.047
}

exp.0307 <- c(31, rep(NA, 24)) 
for(i in 2:25){
    exp.0307[i] <- exp.0307[i-1] + exp.0307[i-1]*.0307
}

@@

years <- c(1989, 2005, 2013, 2013)
points <- c(31, n.journals.year$Journal.count[c(17,25)], max(n.journals.year$exp.05))
annotate.df <- data.frame(years, points)

@@

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2014.5, y = 60, label = "3.07% CAGR", size = 4) +
    annotate("text", x = 2016, y = 74.5, label = "Linear growth", size = 4) + 
    annotate("text", x = 2015.5, y = 95, label = "4.7% CAGR", size = 4) + 
    annotate("text", x = 2016.5, y = 67, label = "Observed growth", size = 4) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))
